Outstanding Title

### 2017-02-23 writing/EpiDraft.Rmd
Complete Simulating Data section.

>>>>

The `eesim` output also gives the relative parameter estimate bias, according to the following equation  from (citet{Beaujean2014}), given $\theta_{H}$ (true value of the parameter, as set when creating the simulated data) and $\hat{\theta}$ (value of the parameter estimated from applying a model to the simulated data):

\begin{equation}
\theta_{bias} = \frac{\hat{\theta} - \theta_{H}}{\theta_{H}}
\end{equation}

Finally, the `eesim` output gives the coverage and power of the model.
